\documentclass[conference,10pt]{IEEEtran}

\usepackage{cite}
\usepackage{url}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

\title{A FAIR Evidence Object Layer for Auditable Agent Self-Improvement}

\author{
\IEEEauthorblockN{AUTHOR\_VERIFY: Author names withheld until human authors decide final submission and single-blind handling}
\IEEEauthorblockA{AUTHOR\_VERIFY: Affiliation and contact information}
}

\begin{document}
\maketitle

\begin{abstract}
AUTHOR\_VERIFY: Rewrite the abstract in human-authored prose. Pull exact
metric language from reports/asiep\_v0.1\_evaluation\_report.json. This file is
an IEEE-style scaffold, not a final submission.
\end{abstract}

\begin{IEEEkeywords}
FAIR evidence object, provenance, agent accountability, reproducibility,
agent self-improvement, validation, RO-Crate, FDO
\end{IEEEkeywords}

\section{Introduction}
AUTHOR\_VERIFY: Move human-rewritten Introduction text here.

\section{Problem and Scope}
AUTHOR\_VERIFY: Preserve local fixture and minimal implementation boundaries.

\section{Requirements for Agent Self-Improvement Evidence}
AUTHOR\_VERIFY: Summarize the agent-readable evidence requirements.

\section{ASIEP Profile and Lifecycle}
AUTHOR\_VERIFY: Verify field names against schemas/asiep.schema.json and
docs/state\_machine.md.

\section{Agent-native Toolchain}
AUTHOR\_VERIFY: Describe validator, repairer, resolver, importer, packager,
and evaluator without expanding ASIEP claims.

\section{Evidence Bundle and Local Packaging}
AUTHOR\_VERIFY: Explain local bundle resolution and package outputs. Do not
claim external certification or registry registration.

\section{Evaluation}
AUTHOR\_VERIFY: Pull exact values from the latest evaluation report. Keep local
fixture limitations visible.

\section{Cross-standard Mapping}
AUTHOR\_VERIFY: Discuss lossiness and cite external sources.

\section{Artifacts and Reproducibility}
AUTHOR\_VERIFY: Decide repository link and anonymization language.

\section{Limitations}
AUTHOR\_VERIFY: Preserve all M0-M10 limits.

\section{Conclusion}
AUTHOR\_VERIFY: Rewrite after page-budget trimming.

\section*{Acknowledgements}
AUTHOR\_VERIFY: If AI-generated content remains in submitted material, disclose
it here. Identify the AI system used, identify sections where AI-generated
content was used, briefly describe the level of use, and state that human
authors are responsible for all submitted content.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
