\section{Conclusion}

This paper presented ASIEP, a minimal FAIR-compatible evidence object profile for auditable agent self-improvement events. The central claim is modest: self-improvement should not be treated only as a runtime trace or an informal log entry, because it changes artifacts that may shape future agent behavior. ASIEP addresses this gap by binding trigger evidence, lineage, candidate changes, validation results, gate decisions, integrity metadata, and rollback references into a lifecycle-aware and reference-bound evidence object.

The local implementation demonstrates that ASIEP can be checked by an agent-readable toolchain. The validator, repair planner, resolver, importer, packager, and evaluator support structured conformance checking, bounded repair planning, digest-bound bundle resolution, local trace import, evidence packaging, and fixture-based evaluation. On the current local corpus, the toolchain distinguishes known valid and invalid records, detects several evidence failures, and produces reusable local research-object packages.

Public source code, local fixtures, paper sources, and evaluation materials for this submission are available in the project repository: \url{https://github.com/joy7758/agent-accountability-evidence-layer}.

The work remains intentionally limited. It does not claim production deployment, external certification, complete governance coverage, live observability integration, real FDO registration, PID issuance, or full RO-Crate certification. Future work should test ASIEP on live traces, extend the corpus across multiple agent frameworks, strengthen cryptographic and privacy controls, evaluate human review workflows, and refine the profile through engagement with provenance, FAIR Digital Object, RO-Crate, observability, and AI governance communities. The broader direction is an Agent Accountability Evidence Layer in which self-improvement is one important profile among other agent-to-agent accountability events.
